---
title: "Example Usage of FARS Functions"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{example-fars}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(trafficR)
```

First we need to create the filename for a given accident data.

```{r make_filename}
#get filename
fname <-make_filename(2013)
fname
file.path("..","data",fname)

```


Next we can read in a single data set using the file name we just created. Each row of the data represents a single accident.


```{r fars_read}
df <- fars_read(fname)
head(df)
```

If you need to read in multiple years just use **fars_read_years**. In the following example only 2013 and 2014.

```{r fars_read_years}
fars_read_years(2013:2014)
```

Now to get the summary of the counts by year we can use the following function.

```{r fars_summarize}
fars_summarize_years(2013:2014)
```

Lastly we will plot map of accidents for California using **fars_map_state**

```{r fars_map_state}
fars_map_state(state.num=6, year=2013)
```
